\bfseries Equivariant convolution-based functions on tensor fields

### 2022-08-01 paper/main.tex
Updates from Overleaf
incorporate new figures

@@

Show all the filters for $d=2$, $M=3$.

Show all the filters for $d=2$, $M=5$.

Show all the filters for $d=3$, $M=3$.

@@

@@

@@

>>>>

%-- is it the same to do convolutions + products + convolutions + products

%-- a counting argument may tell us that all the linear functions that are equivariant  (Molien's formula)

%-- BEN: compute Molien's formula for this (translations semidirect D_4) action
% 1/|G|\sum_{g\in G} det(I-\phi(g)t)^{-1}

@@

\begin{figure}[tp]
\includegraphics[width=\textwidth]{notebooks/filter+0_2_3.png}\\
\includegraphics[width=\textwidth]{notebooks/filter+1_2_3.png}\\
\includegraphics[width=\textwidth]{notebooks/filter-1_2_3.png}
\caption{All the filters for $d=2$, $m=1$. HOGG: notes!}
\end{figure}

\begin{figure}[tp]
\includegraphics[width=\textwidth]{notebooks/filter+0_2_5.png}\\
\includegraphics[width=\textwidth]{notebooks/filter-0_2_5.png}\\
\includegraphics[width=\textwidth]{notebooks/filter+1_2_5.png}\\
\includegraphics[width=\textwidth]{notebooks/filter-1_2_5.png}
\caption{All the filters for $d=2$, $m=2$. HOGG: notes!}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{notebooks/monomials_1.png}
    \caption{A scalar image $s$ and convolutions with four chosen filters.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{notebooks/monomials_2.png}
    \caption{All unconvolved second-degree monomials of $s$, given four chosen filters. For the 2-tensor outputs (order $k=2$), we traced them back to scalars.}
\end{figure}

@@

\paragraph{Acknowlegements:}
This project made use of Python, numpy, matplotlib, and cmastro.
